Distributed Tic Tac Toe:\\ Peer-to-Peer Team-Based Gaming System

### 2017-11-23 paper/paper.tex

The leaders communicate the vote of their team to the opposing leader so that they may pass that result on to the peers of that team, as pictured in figure 1.
\section{Implementation}
The implementation follows the RMI distributed object model. A GameInt interface extends java.rmi.Remote and lists remote classes. 
A Game class implements GameInt and extends the UnicastRemoteObject. It is an analogy for what a player knows and does during a game. 
It provides an implementation for all the listed classes in the interface which include the functionality of requesting the player to make a play, 
setting the leader of the game, several methods to interact with the Role of the player and a main method that connects to other game instances. 
Currently, when running the game, the user passes it a local instance name and the name of another instance as arguments. Each instance then uses this information 
to do an RMI Registry lookup and get a reference to the other client. The Role interface allows the application to differentiate between Leader and Player classes which extend it. 
It utilises the State design pattern to allow players to seamlessly have their role changed – for example when the current leader disconnects. 
A Leader is responsible of collecting the votes from all of the members in their team in the turnStarts() method. This is done asynchronously using
a separate thread for each member – an instance of VoteThread. Each thread collects a vote from one assigned player then writes it into a corresponding position
in a shared AtomicIntegerArray that they have all been passed by the Leader. This ensures the main Leader thread can then read these values. 
Each Leader then informs all players in the game about the vote of his team. A Player instance represents a regular player that only must vote. 
Each regular player also has a mechanism to detect if a leader has not contacted them to choose a play for too long. If a time-out is triggered, 
a player calls for a new leader election. To avoid many simultaneous election calls, each regular player waits 5 minutes plus a randomised amount of time.
All plays are recorded on a GameState object instance that acts as a game board. After each turn it checks if the game is over and relays this message to the leaders
 which can then inform the members of their team.
\section{Evaluation}

>>>>

The leaders communicate the vote of their team to the opposing leader so that they may pass that result on to the peers of that team, as pictured in figure 1.

By considering the fact that only the two leaders communicate about the votes between the two teams, then the system can easily break if one of the leaders creashes. 
In order to avoid that and provide a more robust system we chose to implemet the Bully Algorithm on each of the players so they will be able to detect a leader crash if they do not receive a vote reply from them in a certain period of time.
After that, they can easily call for an election on older processes than them and wait for a leader to be announced on a different period of time.
If no leader is announced on that period of time or there are no older processes, then that process can declare itself leader to the rest of the team and the opponent leader.

\section{Implementation}

The implementation follows the RMI distributed object model. A GameInt interface extends java.rmi.Remote and lists remote classes. 
A Game class implements GameInt and extends the UnicastRemoteObject. It is an analogy for what a player knows and does during a game. 
It provides an implementation for all the listed classes in the interface which include the functionality of requesting the player to make a play, 
setting the leader of the game, several methods to interact with the Role of the player and a main method that connects to other game instances. 
Currently, when running the game, the user passes it a local instance name and the name of another instance as arguments. Each instance then uses this information 
to do an RMI Registry lookup and get a reference to the other client. The Role interface allows the application to differentiate between Leader and Player classes which extend it. 
It utilises the State design pattern to allow players to seamlessly have their role changed – for example when the current leader disconnects. 
A Leader is responsible of collecting the votes from all of the members in their team in the turnStarts() method. This is done asynchronously using
a separate thread for each member – an instance of VoteThread. Each thread collects a vote from one assigned player then writes it into a corresponding position
in a shared AtomicIntegerArray that they have all been passed by the Leader. This ensures the main Leader thread can then read these values. 
Each Leader then informs all players in the game about the vote of his team. A Player instance represents a regular player that only must vote. 
Each regular player also has a mechanism to detect if a leader has not contacted them to choose a play for too long. If a time-out is triggered, 
a player calls for a new leader election. To avoid many simultaneous election calls, each regular player waits 5 minutes plus a randomised amount of time.
All plays are recorded on a GameState object instance that acts as a game board. After each turn it checks if the game is over and relays this message to the leaders
 which can then inform the members of their team.

% Bully Implementation
% All of the players keep track of their leader, the opponent leader and a priority list of their team.
% In this case, they can easily use the list to start election on the processes older than them.

\section{Evaluation}
